D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-06 ootavacuous.tex
"Non-Trivial Semantic Dependencies": Distinguish init from input
Initial values are part of the program, so talk instead about the
alternative case where those values were taken as input by a single
program.

Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Starting with the intuitive execution where the values loaded from \co{x}
and \co{y} on lines~9 and~10 are the value 1 (that is, nonzero), executions
that differ only in the value loaded from either \co{x} or \co{y} will
still affect the value stored to \co{z} by line~11.
There is therefore one semantic dependency from the load from \co{x}
to the store to \co{z} and another separate semantic dependency from
the load from \co{y} to the store to \co{z}, which matches typical
definitions of semantic dependency.
Yet
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and
Listing~\ref{lst:OOTA Multiplication Example, Initial Value 1}
can be thought of as being two different executions of the exact same
program.

>>>>

Starting with the intuitive execution where the values loaded from \co{x}
and \co{y} on lines~9 and~10 are the value 1 (that is, nonzero), executions
that differ only in the value loaded from either \co{x} or \co{y} will
still affect the value stored to \co{z} by line~11.
There is therefore one semantic dependency from the load from \co{x}
to the store to \co{z} and another separate semantic dependency from
the load from \co{y} to the store to \co{z}, which matches typical
definitions of semantic dependency.
Yet if the initial values were instead obtained as input,
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and
Listing~\ref{lst:OOTA Multiplication Example, Initial Value 1}
could be thought of as being two different executions of the exact same
program.
